\begin{intro}
  \begin{tabular}[t]{@{}lllll}
  |_{C#m} & |_{B} & |_{F#} & | _{F#} & | \\
\end{tabular}
\end{intro}

\begin{verse}
^{C#m} Dog goes ^{B}woof, cat goes ^{F#}meow, bird goes ^{F#}tweet, and mouse goes ^{C#m}squeek \\
Cow goes ^{B}moo, frog goes ^{F#}croak, and the ^{F#}elephant goes toot ^{C#m} \\
Ducks says quack, ^{B} and fish go ^{F#}blub  and the seal goes ^{F#}ow ow ow ^{C#m} \\
But there's one sound ^{B} that no one ^{F#}knows... ^{F#} What does the fox say?
\end{verse}

\begin{chorus}
^{C#m}Ring-ding-ding-ding-dingeringding! ^{C#m}Gering-ding-ding-ding-dingeringding! 
^{C#m}Gering-ding-ding-ding-dingeringding!
^{F#} What the fox say? \\
^{C#m}Wa-pa-pa-pa-pa-pa-pow! ^{C#m}Wa-pa-pa-pa-pa-pa-pow! ^{C#m}Wa-pa-pa-pa-pa-pa-pow!
^{F#} What the fox say? \\
^{C#m}Hatee-hatee-hatee-ho! ^{C#m}Hatee-hatee-hatee-ho! ^{C#m}Hatee-hatee-hatee-ho!
^{F#} What the fox say? \\
^{C#m}Joff-tchoff-tchoffo-tchoffo-tchoff! ^{C#m}Joff-tchoff-tchoffo-tchoffo-tchoff! 
^{C#m}Joff-tchoff-tchoffo-tchoffo-tchoff! ^{F#} What the fox say?
\end{chorus}

\begin{verse}
^{C#m} Big blue ^{B}eyes, pointy ^{F#}nose, chasing ^{F#}mice and digging ^{C#m}holes \\
Tiny ^{B}paws, up the ^{F#}hill, sudden^{F#}ly you're standing still \\
^{C#m} Your fur is red, ^{B} so beautiful, ^{F#} like an ^{F#}angel in disguise  \\
^{C#m} But if you meet ^{B} a friendly horse, ^{F#} will you com^{F#}municate by \\
^{C#m}mo-o-o-o-orse? ^{B}Mo-o-o-o-orse? ^{F#}Mo-o-o-o-orse? How will ^{F#}you speak to that \\
^{C#m}ho-o-o-o-orse? ^{B}Ho-o-o-o-orse? ^{F#}Ho-o-o-o-orse? ^{F#} What does the fox say?
\end{verse}

\begin{chorus}
^{C#m}Jacha-chacha-chacha-chow! ^{C#m}Chacha-chacha-chacha-chow! ^{C#m}Chacha-chacha-chacha-chow!
^{F#} What the fox say? \\
^{C#m}Fraka-kaka-kaka-kaka-kow! ^{C#m}Fraka-kaka-kaka-kaka-kow! ^{C#m}Fraka-kaka-kaka-kaka-kow!
^{F#} What the fox say? \\
^{C#m}Ah-hee-ahee ha-hee! ^{C#m}Ah-hee-ahee ha-hee! ^{C#m}Ah-hee-ahee ha-hee!
^{F#} What the fox say? \\
^{C#m}Ah-oo-oo- ^{C#m}oo-ooo! ^{C#m}Woo-oo-oo-ooo!
^{F#} What does the fox say?
\end{chorus}

\begin{outro}
^{A} The se^{A-}cret of ^{G#m}the \hspace{10pt} ^{C#m}fox... \hspace{10pt} ^{C#m}ancient myste^{B}ry... \hspace{10pt}
^{B-}somewhere ^{G#m}deep  in the ^{A}woods \\
I ^{A-}know you're ^{B}hiding... ^{A} \hspace{10pt} ^{A-}What ^{G#m}is your ^{C#m}sound? \hspace{10pt} ^{C#m}Will we ever ^{B}know? 
Will ^{B-}always be a ^{G#m}myste- ^{A}ry \\ 
^{A}What do you ^{A}say? ^{A-} ^{G#m} \hspace{10pt} ^{C#m} 
^{C#m}You're my guardian ^{B}angel ^{B-}hiding ^{G#m}in the ^{A}woods \\
^{A-}What ^{B}is your ^{A}sound? (Abub-bub-bub-way-dum) ^{A-}(Abubidi- ^{G#m}bi- bum-way-^{C#m}dum) \\
(Abub-bub-bub-way-dum) ^{C#m}Will we ever ^{B}know? \\
(Babeh-dih-bah-top-beh-dum) ^{B-}I want ^{G#m}to... \\
(Bahbeh-dum-beh-dum) ^{A}I want to... ^{A}I want to ^{C#m}know! (Ababeh-dih-bah-bum-beh-dum)
\end{outro}