\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Part of Your World}, band={The Little Mermaid}, year={1989}, key={F}}

  \begin{intro}
    "Maybe he's right... maybe there is something the matter with me." \\
    \begin{tabular}[t]{@{}lllll}
      |_{Bb} & |_{C} & |_{Bb} & |_{C} & | "I just don't see how a world that makes such wonderful things could be bad."
    \end{tabular}
  \end{intro}

  \begin{verse}
    ^{Bb}Look at this stuff, ^{C}isn't it neat? \hspace{20pt}
    ^{Bb}Wouldn't you think my col^{C}lection's complete? \\
    ^{Am}Wouldn't you think I'm the ^{Dm}girl, \hspace{20pt}
    the girl who ^{G}has everything? \hspace{10pt} ^{G} \\
    ^{Bb}Look at this trove, ^{C}treasures untold \hspace{20pt}
    ^{Bb}How many wonders can ^{C}one cavern hold? \\
    ^{Am}Lookin' around here you'd ^{Dm}think,
    "Sure, ^{G}she's got everything" \hspace{10pt} ^{G}
  \end{verse}

  \begin{bridge}
    I've got ^{Bb}gadgets and gizmos ap^{Am}lenty \hspace{20pt}
    I've got ^{Dm}whozits and whatzits ga^{G}lore \\
    You want ^{Bb}thingamabobs? I got ^{Am}twenty \hspace{20pt}
    But who ^{Dm}cares? No big ^{G}deal, \instruction{pause} I want ^{C}more \hspace{10pt} ^{C}
  \end{bridge}

  \begin{verse}
    ^{F}I want to be where the ^{Am}people are \hspace{20pt}
    ^{Bb}I want to see want to ^{C}see 'em dancin' \\
    ^{Dm}Walkin' around on those... ^{Am} What do you call 'em? ^{C} Oh, feet ^{C} \\
    ^{F}Flippin' your fins you don't ^{Am}get too far \hspace{20pt}
    ^{Bb}Legs are required for ^{C}jumpin', dancin' \\
    ^{Dm}Strollin' along down a... ^{Am} What's that word again? ^{C} ... Street ^{C}
  \end{verse}

  \begin{chorus}
    Up where they ^{F}walk, up where they ^{F7}run \hspace{20pt}
    Up where they ^{Bb}stay all day in the ^{Bbm}sun \\
    Wanderin' ^{F}free, wish I could ^{C}be part of that ^{F}world \hspace{10pt} ^{F}
  \end{chorus}

  \begin{bridge}
    What would I ^{Bb}give if I could ^{C}live outta these ^{Am}waters? ^{Dm}   \\
    What would I ^{Bb}pay to spend a ^{C}day warm on the ^{Am}sand? ^{Dm}   \\
    Betcha on ^{Bb}land they under^{C}stand, bet they don't ^{Am}reprimand their ^{Dm}daughters \\
    Bright young ^{G}women sick of ^{G}swimming ready to ^{Eb}stand ^{C}
  \end{bridge}

  \begin{verse}
    And ^{F}ready to know what the ^{F7}people know \hspace{20pt}
    ^{Bb}Ask 'em my questions and ^{C}get some answers \\
    ^{Dm} What's a fire and ^{Am}why does it... what's the word? ... ^{C} Burn? ^{C}
  \end{verse}

  \begin{chorus}
    When's it my ^{F}turn? Wouldn't I ^{F7}love, love to ex^{Bb}plore that shore up a^{Bbm}bove? \hspace{20pt} ^{Bbm} \\
    \instruction{slowly} ^{N.C.} Out of the ^{F*}sea, wish I could ^{C*}be part of that ^{(Bb)}world
  \end{chorus}

  \begin{outro}
    \begin{tabular}[t]{@{}lllll}
      |_{Bb} & |_{C} & |_{Bb} & |_{C} & | \\
      |_{F*} & |
    \end{tabular}
  \end{outro}
\end{song}
\end{document}
