\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Mr. Blue Sky}, band={Electric Light Orchestra}, year={1977}, key={F}}

  \begin{intro}
    \begin{tabular}[t]{@{}lllll}
      |_{F} & |_{F} & | \\
    \end{tabular}
  \end{intro}

  \begin{verse}
    ^{F}Sun is shining ^{F}in the sky, ^{F} there ain't a ^{Em7-}cloud ^{A}in ^{Dm}sight,
    it stopped ^{G}raining \\
    Every^{Em}body's in a ^{A}play and don't you ^{Bb}know, it's a ^{C}beautiful new ^{F}day, hey  ^{C}  \\
    ^{F}Running down the ^{F}avenue, ^{F} see how the ^{Em7-}sun ^{A}shines ^{Dm}brightly in the ^{G}city \\
    On the ^{Em}streets where once was ^{A}pity Mr. ^{Bb}Blue Sky is ^{C}living here ^{F}today, hey ^{C}
  \end{verse}

  \begin{chorus}
    \instruction{Do this 2x} \\
    ^{Dm} Mr. Blue ^{Dm/C}Sky please tell us ^{Bbmaj7}why, you had to
      ^{Bbmaj7/A}hide away for ^{Gm}so long, ^{F} where did ^{Eb}we go wrong? ^{Bb}
  \end{chorus}

  \begin{solo}
    \begin{tabular}[t]{@{}lllll}
      |_{C}  & |_{C}  & |                       \\
      |_{F}  & |_{F}  & | _{F} & | _{Em7-A} & | \\
      |_{Dm} & |_{G}  & |_{Em} & | _{A}     & | \\
      |_{Bb} & | _{C} & |_{F}  & | _{C}     & |
    \end{tabular}
  \end{solo}

  \begin{verse}
    ^{F} Hey you with the ^{F}pretty face ^{F}welcome to the ^{Em7-}hu- ^{A}man ^{Dm}race, a celeb^{G}ration \\
    Mr. ^{Em}Blue Sky's up there ^{A}waiting and to^{Bb}day is the ^{C}day we've waited ^{F}for, aaahh ^{C}
  \end{verse}

  \begin{chorus}
    ^{Dm} Mr. Blue ^{Dm/C}Sky please tell us ^{Bbmaj7}why, you had to
      ^{Bbmaj7/A}hide away for ^{Gm}so long, ^{F} where did ^{Eb}we go wrong? ^{Bb}
  \end{chorus}

  \begin{chorus}
    \instruction {do this 2x} \\
    ^{Dm}Hey there ^{Dm/C}Mr. Blue ^{Bbmaj7}we're so pleased to ^{Bbmaj7/A}be with you \\
    ^{Gm}Look around see ^{F}what you do, ^{Eb}everybody ^{Bb}smiles at you
  \end{chorus}

  \begin{interlude}
    \begin{tabular}[t]{@{}lllll}
      |_{C}                   & |_{C}  & |                                         \\
      |_{F} (Mr. Blue Sky...) & |_{F}  & | _{F} & | _{Em7-A} (Mr. Blue Sky...) & | \\
      |_{Dm}                  & |_{G}  & |_{Em} & | _{A} (Mr. Blue Sky...)     & | \\
      |_{Bb}                  & | _{C} & |_{F}  & | _{C}                       & |
    \end{tabular}
  \end{interlude}

  \begin{verse}
    ^{F}Mr. Blue you ^{F}did it right ^{F} but soon comes ^{Em7-}Mis- ^{A}ter ^{Dm}Night,
    creeping ^{G}over now his ^{Em}hand is on your ^{A}shoulder never^{Bb}mind
    I'll re^{C}member you this, ^{C#}  I'll re^{Eb}member you this ^{(Dm)}way
  \end{verse}

  \begin{chorus}
    ^{Dm} Mr. Blue ^{Dm/C}Sky please tell us ^{Bbmaj7}why, you had to
      ^{Bbmaj7/A}hide away for ^{Gm}so long, ^{F} where did ^{Eb}we go wrong? ^{Bb} \\
    ^{Dm}Hey there ^{Dm/C}Mr. Blue ^{Bbmaj7}we're so pleased to ^{Bbmaj7/A}be with you \\
    ^{Gm}Look around see ^{F}what you do, ^{Eb}everybody ^{Bb}smiles at you
  \end{chorus}


  \begin{outro}
    \instruction{repeat chorus chords and solo until end} \\
    \begin{tabular}[t]{@{}lllll}
      |_{Dm} & |_{Dm/C} & | _{Bbmaj7} & | _{Bbmaj7/A} & | \\
      |_{Gm} & |_{F}    & |_{Eb}      & | _{Bb}       & |
    \end{tabular} \\
    \instruction{end on F}
  \end{outro}

\end{song}
\end{document}