\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Make Me Feel}, band={Janelle Monae}, year={2018}, key={B}}

  \begin{intro}
    _{F#7}
  \end{intro}

  \begin{verse}
    Baby, don't ^{F#7}make me spell it out for you, all of the ^{F#7}feelings that I've got for you \\
    Can't be ^{Bsus4}explained, but I can try for you. Yeah, baby, don't ^{F#7}make me spell it out for you \\
    You keep on ^{F#7}asking me the same questions and second ^{F#7}guessing all my intentions \\
    Should know by the ^{Bsus4}way I use my compression you've got the ^{F#7}answers to my confessions
  \end{verse}

  \begin{prechorus}
    It's like I'm ^{C#5}powerful with a little bit of tender. ^{B5}An emotional, sexual bender \\
    ^{D#5}Mess me up, yeah, but no one does it better. ^{C#5}There's nothing better...
  \end{prechorus}

  \begin{chorus}
    That's just the way you make me ^{F#7}feel (that's just the way you make me feel) \\
    That's just the way you make me ^{F#7}feel (that's just the way you make me feel) \\
    So good, so good, so fucking ^{Bsus4}real (that's just the way you make me feel) \\
    That's just the way you make me ^{F#7}feel (that's just the way you make me feel) \\
    That's just the way you make me feel
  \end{chorus}

  \begin{verse}
    You know I ^{F#7}love it, so please don't stop it. You got me ^{F#7}right here in your jean pocket \\
    Laying your ^{Bsus4}body on a shag carpet. You know I ^{F#7}love it so please don't stop it
  \end{verse}

  \begin{prechorus}
    \instruction{repeat Prechorus}
  \end{prechorus}

  \begin{chorus}
    \instruction{repeat Chorus}
  \end{chorus}

  \begin{bridge}
    ^{F#7} HUH! That's just the way that I ^{F#7}feel now, baby... Good God! I can't help ^{Bsus4}it, ugh! \\
    That's just the way that I ^{F#7}feel, yeah... Please! I can't help it!
  \end{bridge}

  \begin{prechorus}
    It's like I'm ^{C#5}powerful with a little bit of tender. ^{B5}An emotional, sexual bender \\
    ^{D#5}Mess me up, yeah, but no one does it better. ^{C#5}There's nothing better... \\
    \instruction{pause} Damn!
  \end{prechorus}

  \begin{outro}
    \instruction{repeat Chorus and fade out}
  \end{outro}

\end{song}
\end{document}
