\begin{intro}
\begin{tabular}[t]{@{}lllll}
  |_{C#} & |_{C#} & |_{C#} & |_{C#} & | \\
\end{tabular}
\end{intro}

\begin{verse}
^{C#}Fox in the snow, ^{G#}where do you go to find ^{A#m}something you could eat? \\
Cause the ^{F#maj7}word out on the street is you are ^{G#}starving \\
Don’t let yourself grow ^{C#}hungry now, ^{F7} don’t let yourself grow ^{A#m}cold, 
fox in the ^{F#maj7}snow ^{C#} \hspace{5pt} ^{F#maj7} \hspace{5pt} ^{C#}
\end{verse}

\begin{verse}
^{C#}Girl in the snow, ^{G#}where do you go to find ^{A#m}someone who will do,
to tell ^{F#maj7}someone all the truth before it ^{G#}kills you? \\
They listen to your ^{C#}crazy laugh ^{F7} before you hang a ^{A#m}right 
and disappear from ^{F#maj7}sight  ^{C#} \\
^{F#maj7}What do they know ^{C#}anyway? You'll read it in a ^{F#maj7}book \\
What do they know ^{C#}anyway? You'll read it in a ^{Fm}book tonight ^{D#} \hspace{5pt} ^{F#maj7} \hspace{5pt} ^{F#maj7} \hspace{5pt} ^{F#maj7} \hspace{5pt} ^{F#maj7}
\end{verse}

\begin{verse}
^{C#}Boy on the bike, ^{G#}what are you like as you ^{A#m}cycle round the town? \\
You're going ^{F#maj7}up, you're going down, you're going ^{G#}nowhere \\
It's not as if they're ^{C#}paying you, ^{F7} It's not as if it's ^{A#m}fun, 
at least not any^{F#maj7}more  ^{C#}  \\ 
^{F#maj7}When your legs are ^{C#}black and blue it's time to take a ^{F#maj7}break, when your legs are ^{C#}black and blue
it's time to take a holiday
\end{verse}

\begin{solo}
\begin{tabular}[t]{@{}lllllllll}
  |_{C#} & |_{A#m} & |_{F#maj7} & |_{C#} & |_{C#} & |_{A#m} & |_{F#maj7} & |_{C#*} & | \\ 
  |_{B} (half measure - 2 beats only) & | _{A#m} & |_{A#m} & | \\  
  |_{F#maj7} & |_{C#} & |_{F#maj7} & |_{C#} & |_{F#maj7} & |_{C#} & |_{F#maj7} & |_{C#} & | \\ 
\end{tabular}
\end{solo}

\begin{verse}
^{C#}Kid in the snow, ^{G#}way to go. It only ^{A#m}happens once a year.
It only ^{F#maj7}happens once a lifetime make the ^{G#}most of it \\
Second just to ^{C#}being born, ^{F7} second to dying ^{A#m}too. 
What else ^{F#maj7}would you do?   ^{C#}  What else ^{F#maj7}would you do?   ^{C#}   \\
What else ^{F#maj7}would you do?   ^{C#}  What else ^{F#maj7}would you do?   ^{C#}   \\
Fox ^{F#maj7}in the snow  (When your legs are looking ^{C#}black and blue) \\
Fox ^{F#maj7}in the snow  (It's not as if they're ^{C#}paying you) \\
Fox ^{F#maj7}in the snow  (When your legs are looking ^{C#}black and blue) \\
Fox ^{F#maj7}in the snow  (It's not as if they're ^{C#}paying you) \\
Fox ^{F#maj7}in the snow,^{C#} fox ^{F#maj7}in the snow   ^{C#} 
\end{verse}

\begin{outro}
  \begin{tabular}[t]{@{}lllll}
    |_{F#maj7} & |_{C#} & |_{F#maj7} & |_{C#} & | \\
    |_{Fm} & |_{D#} & |_{F#maj7} & | \\
  \end{tabular}
\end{outro}
