\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Rock 'n' Roll Lifestyle}, band={Cake}, year={1994}, key={A}}

  \begin{intro}
    \begin{tabular}[t]{@{}lllllll}
      |_{E} & |_{A} & |_{B-A} & |_{E-A-B} & |
    \end{tabular}
  \end{intro}

  \begin{verse}
    Well, your ^{E}CD collection looks ^{A}shiny and costly,
    ^{B-}how much did you ^{A}pay for your ^{E-}Bad Moto ^{A-B}Guzzi? \\
    And ^{E}how much did you spend on your ^{A}black leather jacket?
    Is it ^{B*}you or your ^{N.C.}parents in this income tax bracket? \\
    ^{E}Now tickets to concerts And ^{A}drinking at clubs,
    ^{B-}sometimes for ^{A}music that you ^{E-}haven't even ^{A-B}heard of \\
    And ^{E}how much did you pay for your ^{A}rock and roll t-shirt
    that ^{B*}proves ^{N.C.}you were there, that you heard of them first?
  \end{verse}

  \begin{chorus}
    Now, ^{E}how do you afford your ^{A}rock 'n' roll lifestyle? \hspace{10pt}
    ^{B-}How do you af^{A}ford your ^{E-}rock 'n' roll ^{A-B}lifestyle? \\
    ^{E* - riff}How do you afford ^{A*}your rock 'n' roll lifestyle? Awww tell me
  \end{chorus}

  \begin{solo}
    \begin{tabular}[t]{@{}lllllllllll}
      |_{E} & |_{A} & |_{B-A} & |_{E-A-B} & |_{E*} (begin riff) & |_{A*} & |_{B} & |_{E} & | \\
      |_{E} & |_{A} & |_{B-A} & |_{E-A-B} & |
    \end{tabular}
  \end{solo}

  \begin{verse}
    ^{E}How much did you pay for the ^{A}chunk of his guitar,
    the one he ^{B-}ruthlessly ^{A}smashed at the ^{E-}end of the ^{A-B}show? \\
    And ^{E}how much will he pay for a ^{A}brand new guitar,
    one which he'll ^{B*}ruthlessly ^{N.C.}smash at the end of another show? \\
    And ^{E}how long will the workers keep ^{A}building him new ones?
    As ^{B*}long as ^{N.C.}their soda cans are red, white, and blue ones \\
    And ^{E}how long will the workers keep ^{A}building him new ones?
    As ^{B*}long as ^{N.C.}their soda cans are red, white, and blue ones
  \end{verse}

  \begin{solo}
    \begin{tabular}[t]{@{}lllllllllll}
      |_{E} & |_{A} & |_{B-A} & |_{E-A-B} & |_{E} & |_{A} & |_{B-A} & |_{E-A-B} & |
    \end{tabular}
  \end{solo}

  \begin{verse}
    ^{E}Aging black leather and ^{A}hospital bills
    and ^{B-}tattoo ^{A}removal and ^{E-}dozens of ^{A-B}pills \\
    Your ^{E}liver pays dearly now for ^{A}youthful magic moments
    but ^{B*}rock on ^{N.C.}completely with some brand new components
  \end{verse}

  \begin{chorus}
    \instruction{repeat Chorus}
  \end{chorus}

  \begin{solo}
    \begin{tabular}[t]{@{}lllllllllll}
      |_{E} & |_{A} & |_{B-A} & |_{E-A-B} & |_{E*} (begin riff) & |_{A*} & |_{B} & |_{E} & |
    \end{tabular}
  \end{solo}

  \begin{outro}
    \instruction{repeat in background: "How do you afford your rock n roll lifestyle?"} \\
    Excess ain't ^{E}rebellion ^{A} You drinkin' what they're ^{B-A}sellin'
    ^{E-} Your self-^{A-B}destruction doesn't ^{E}hurt them \\
    ^{A} Your chaos won't convert ^{B-A}them
    ^{E-} They're ^{A-B}so happy to re^{E}build it
      ^{A} You'll never really ^{B-A}kill it \\
    ^{E-} Exc^{A-B}ess ain't ^{E}rebellion ^{A} You drinkin' what they're ^{B-A}sellin?
    ^{E-} Exc^{A-B}ess ain't ^{E}rebellion \\
    ^{A} You drinkin', you're ^{B-A}drinking ^{E-} You're ^{A-B}drinkin' what they're... ^{E* - riff}sellin' \hspace{10pt} ^{A*} \hspace{10pt} ^{B} \hspace{10pt} ^{E} \\
    Al^{E* - riff}right!  Aw! ^{A*}  Yeah!^{B*} \hspace{10pt} ^{B} Alllllllll^{E*}right!
  \end{outro}

\end{song}
\end{document}
