\begin{intro}
  \begin{tabular}[t]{@{}lllll}
  |_{Fm} & |_{Db} & |_{Eb} & |_{Bbm} & | \\
  |_{Fm} & |_{Db} & |_{Eb} & |_{Bb} & | 
  \end{tabular}
\end{intro}

\begin{verse}
The ^{Fm}snow glows white on the ^{Db}mountain tonight,
not a ^{Eb}footprint to be seen^{Bbm} \\
A ^{Fm}kingdom of ^{Db}isolation
and it ^{Eb}looks like I'm the ^{Bb}queen \\      
^{Fm} The wind is ^{Db}howling like this ^{Eb}swirling storm inside^{Bbm} \\
^{Fm} Couldn't keep it in, ^{Db} heaven knows I've ^{Bb}tried
\end{verse}

\begin{prechorus}
^{Eb}Don't let them in, don't let them ^{Db}see. 
Be the good girl you always have to ^{Eb}be \\
Conceal, don't feel, don't let them ^{Db}know...
Well, now they know!
\end{prechorus}

\begin{chorus}
Let it ^{Ab}go,  Let it ^{Eb}go,
Can't ^{Fm}hold it back ^{Db}anymore \\
Let it ^{Ab}go,  Let it ^{Eb}go,
Turn aw^{Fm}ay and slam the ^{Db}door \\
^{Ab}I don't ^{Eb}care what they're ^{Fm}going to ^{Db}say \\
Let the ^{Cm}storm rage ^{B}on...
The ^{Dbsus2*}cold never bothered me anyway  
\end{chorus}

\begin{verse}
^{Ab} ^{Eb} ^{Fm}It's funny how some ^{Db}distance
makes ^{Dbsus2}everything seem ^{Bbm}small \\
^{Fm}And the fears that once controlled^{Eb}  me can't ^{Bb}get to me at all
\end{verse}

\begin{prechorus}
^{Eb}It's time to see what I can ^{Db}do, 
to test the limits and break ^{Eb}through \\
No right, no wrong, no rules for me^{Dbsus2}... I'm free!
\end{prechorus}

\begin{chorus}
Let it ^{Ab}go,  Let it ^{Eb}go,
I'm ^{Fm}one with the wind and ^{Db}sky.
Let it ^{Ab}go,  Let it ^{Eb}go,
You'll ne^{Fm}ver see me ^{Db}cry \\
^{Ab}Here I ^{Eb}stand and ^{Fm}here I ^{Db}stay. 
Let the ^{Cm}storm rage ^{B}on... ^{Db}
\end{chorus}

\begin{bridge}
^{Db}My power flurries through the air into the ground. 
My soul is spiraling in frozen fractals all around \\
^{Eb}And one thought crystallizes like an icy blast. 
^{Fm}I'm never ^{Db}going back, the ^{Eb}past is in the past^{Bbm} ^{Db}
\end{bridge}

\begin{chorus}
Let it ^{Ab}go,  Let it ^{Eb}go,
I'll ^{Fm}rise like the break of ^{Db}down. 
Let it ^{Ab}go,  Let it ^{Eb}go,
That per^{Fm}fect girl is ^{Db}gone \\
^{Ab}Here I ^{Eb}stand in the ^{Fm}light of ^{Db}day. 
Let the ^{Cm}storm rage ^{B}on... 
The ^{Dbsus2*}cold never bothered me anyway
\end{chorus}
