\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Crazy}, band={Gnarls Barkley}, year={2006}, key={Cm}}

  \begin{verse}
    ^{Cm}I remember when, I remember I remember when I lost my mind^{D#maj7} \\
    There was something so pleasant about that ^{G#}place \\
    Even your emotions had an echo in so much ^{Gsus4}space ^{G} \\
    ^{Cm}And when you're out there, without care, yeah I was out of touch^{D#maj7} \\
    But it wasn't because I didn't know ^{G#}enough \\
    I just knew too ^{Gsus4}much ^{G}
  \end{verse}

  \begin{chorus}
    Does that make me ^{Cm}crazy? Does that make me ^{D#}crazy?
    Does that make me ^{G#}crazy? Possibly^{Gsus4} ^{G}
  \end{chorus}

  \begin{bridge}
    ^{C}And I hope that you are having the time of your ^{G#}life
    But think ^{D#maj7}twice, that's my only ^{Gsus4}advice ^{G}
  \end{bridge}

  \begin{verse}
    ^{Cm}Come on now, who do you, who do you, who do you, who do you think you ^{D#maj7}are? \\
    Ha ha ha bless your ^{G#}soul, you really think you're in ^{Gsus4}control? ^{G}
  \end{verse}

  \begin{chorus}
    Well I think you're ^{Cm}crazy! I think you're ^{D#}crazy!
    I think you're ^{G#}crazy just like me^{Gsus4} ^{G}
  \end{chorus}

  \begin{bridge}
    ^{C}My heroes had the heart to lose their lives out ^{G#}on a limb \\
    And all I ^{D#maj7}remember is thinking, I want to ^{Gsus4}be like ^{G}them
  \end{bridge}

  \begin{verse}
    ^{Cm}Ever since I was little, ever since I was little it looked like fun^{D#maj7} \\
    And it's no coincidence I've ^{G#}come and I can die when I'm ^{Gsus4}done ^{G}
  \end{verse}

  \begin{chorus}
    Maybe I'm ^{Cm}crazy? Maybe you're ^{D#maj7}crazy?
    Maybe we're ^{G#}crazy? Probably^{Gsus4} ^{G}
  \end{chorus}

  \begin{outro}
    _{Cm} \space\space\space\space _{G#} \space\space\space\space
    _{D#maj7} \space\space\space\space _{Gsus4} \space\space\space\space
    _{G} \space\space\space\space \\
    _{Cm}  \space\space\space\space

  \end{outro}

\end{song}
\end{document}
