\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Kill Bill}, band={SZA}, year={2022}, key={Ab}}

  \begin{intro}
    \begin{tabular}[t]{@{}lllll}
      |_{Bbm} & |_{Eb} & |_{Ab} & |_{F7} & | \\
    \end{tabular}
  \end{intro}

  \begin{verse}
    ^{Bbm} I'm still a ^{Eb}fan even though I was salty \\
    Hate to see you ^{Ab}with some other broad, know you happy.
    Hate to see you ^{F7}happy if I'm not the one drivin' \\
    I'm so ma^{Bbm}ture, I'm so mature, I'm so ma^{Eb}ture, I got me a therapist to tell me there's other men \\
    I ^{Ab}don't want none, I just want you. If ^{F7}I can't have you, no one should, I ^{Bbm}might
  \end{verse}

  \begin{chorus}
    I might kill my ^{Eb}ex, not the best i^{Ab}dea. His new girlfriend's ^{F7}next, how'd I get ^{Bbm}here? \\
    I might kill my ^{Eb}ex, I still love him, ^{Ab}though. Rather be in ^{F7}jail than alone
  \end{chorus}

  \begin{verse}
    ^{Bbm} I get the sense that it's a lost cause.
      ^{Eb} I get the sense that you might really love her \\
    ^{Ab} The text gon' be evidence, this text is evidence.
    I ^{F7}try to ration with you, no murders, no crimes of passion \\
    But damn ^{Bbm} you was out of reach. You was at the ^{Eb}farmer's market with your perfect peach \\
    Now I'm in a^{Ab}mazement, playin' on my patience.
    Now you layin' ^{F7}facedown, got me singin' over a beat \\
    I'm so ma^{Bbm}ture, I'm so mature, I'm so ma^{Eb}ture,
    I got me a therapist to tell me there's other men \\
    I ^{Ab}don't want none, I just want you. If ^{F7}I can't have you, no one will, I ^{Bbm}
  \end{verse}

  \begin{chorus}
    I might kill my ^{Eb}ex, not the best i^{Ab}dea.
    His new girlfriend's ^{F7}next, how'd I get ^{Bbm}here? \\
    I might kill my ^{Eb}ex, I still love him, ^{Ab}though.
    Rather be in ^{F7}jail than alone
  \end{chorus}

  \begin{bridge}
    ^{Bbm} I did it all for love,
    ^{Eb}  I did it all on no drugs \\
    ^{Ab}  I did all of this sober,
    ^{F7}  I did it all for us \\
    ^{Bbm}Oh, I did it all for love,
    ^{Eb}  I did all of this on no drugs \\
    ^{Ab}  I did all of this sober.
      ^{F7}  Don't you know I did it all for us?
  \end{bridge}

  \begin{chorus}
    ^{Bbm}Oh, I just killed my ^{Eb}ex, not the best i^{Ab}dea.
    Killed his girlfriend ^{F7}next, how'd I get ^{Bbm}here? \\
    I just killed my ^{Eb}ex, I still love him, ^{Ab}though.
    Rather be in ^{F7}hell than alone
  \end{chorus}

\end{song}
\end{document}
