\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Kiss Off}, band={Violent Femmes}, year={1983}, key={Em}}

  \begin{intro}
    _{Em}
  \end{intro}

  \begin{verse}
    I ^{Em}need someone a person to talk to someone who'd care to love \hspace{10pt}
    Could it be ^{C}you? could it be ^{Em}you? \\
    ^{Em}Situation gets rough then I start to panic, it's not enough it's just a habit \\
    Hey kid you're ^{C}sick, darling this is ^{Em}it
  \end{verse}

  \begin{chorus}
    ^{C}You can all just ^{D}kiss off into the ^{C}air \hspace{10pt}
    Behind my ^{D}back I can see them ^{C}stare \\
    They'll hurt me ^{D}bad but I won't ^{C}mind \hspace{10pt}
    They'll hurt me ^{D}bad they do it all the ^{C}time, yeah ^{D}yeah! \\
    Yeah they do it all the ^{C}time  Yeah, ^{D}yeah! \hspace{10pt}
    They do it all the ^{C}time, do it all the ^{D}time \\
    They do it all the ^{C}time, do it all the ^{D}time \hspace{10pt}
    They do it all the ^{C}time, do it all the ^{D}time  ^{Em}
  \end{chorus}

  \begin{verse}
    ^{Em} I hope you know that this will go down on your permanent record... Oh yeah? \\
    Well don't get so dist^{C}ressed, did I happen to mention I'm impressed? ^{Em}
  \end{verse}

  \begin{solo}
    \begin{tabular}[t]{@{}lllll}
      |_{Em} & |_{Em} & |_{Em} & |_{Em} & |
    \end{tabular}
  \end{solo}

  \begin{bridge}
    ^{Em}\instruction{muted strum} \\
    I take 1, 1, 1 cuz you left me \\
    2, 2, 2 for my family and \\
    3, 3, 3 for my heartache and \\
    4, 4, 4 for my headaches and \\
    5, 5, 5 for my lonely and \\
    6, 6, 6 for my sorrow and \\
    7, 7 for no tomorrow and \\
    8, 8, I forget what 8 was for and \\
    9, 9, 9 for a lost god but \\
    10, 10, 10, 10 for everything everything everything everything
  \end{bridge}

  \begin{chorus}
    Well ^{C}you can all just ^{D}kisss off into the ^{C}air \hspace{10pt}
    Behind my ^{D}back I can see them ^{C}stare \\
    They'll hurt me ^{D}bad but I won't ^{C}mind \hspace{10pt}
    They'll hurt me ^{D}bad they do it all the ^{C}time, yeah ^{D}yeah! \\
    Yeah they do it all the ^{C}time  Yeah, ^{D}yeah! \hspace{10pt}
    They do it all the ^{C}time, do it all the ^{D}time \\
    They do it all the ^{C}time, do it all the ^{D}time \hspace{10pt}
    They do it all the t^{C}ime, do it all the ^{D}time   ^{Em}
  \end{chorus}

\end{song}
\end{document}
