\begin{intro}
    \begin{tabular}[t]{@{}lllll}
        |_{G#} & |_{C#} & |_{F#-} & |_{F#} & | \\
        |_{G#} & |_{C#} & |_{F#-} & |_{F#} & | \\
        |_{G#} & |_{C#} & |_{F#-} & |_{F#} & | \\
        |_{G#} & |_{C#} & |_{F-} & |_{F} Domo arigato Mr. Roboto... (\domoarigato) & | 
    \end{tabular}
    \begin{tabbing}
        \textbf{} \=^{F}Domo arigato Mr. Roboto, \hspace{10pt} \=^{F#}mata au hi made \\
        \textbf{} \>\domoarigato \>\mata \\
        \textbf{} \=^{F}Domo arigato Mr. Roboto, \hspace{10pt} \=^{F#}himitsu o shiritai \\
        \textbf{} \>\domoarigato \>\himitsu
    \end{tabbing}
\end{intro}

\begin{prechorus}
You're ^{G#}wondering ^{C#}who I ^{F#}am (secret secret, I got a secret) \hspace{10pt}
Mac^{G#}hine ^{C#}or manneq^{F#}uin (secret secret, I got a secret) \\
With par^{G#}ts made ^{C#}in Ja^{F#}pan (secret secret, I got a secret) \hspace{10pt}
I a^{G#}m the mo^{C#}dern ^{D#m}man \hspace{10pt} ^{D#m} \hspace{10pt} ^{D#m} \hspace{10pt} ^{D#m}
\end{prechorus}

\begin{verse}
^{D#m}I've got a secret, ^{D#m}I've been hiding, ^{C#}under my skin ^{C#-} ^{Dm}  \\
^{D#m}My heart is human, ^{D#m}my blood is boiling, ^{C#}my brain I.B.M.^{C#-} ^{Dm} \\
^{D#m}So if you see me, ^{D#m}acting strangely, ^{C#}Don't be surprised ^{C#-} ^{Dm} \\
^{D#m}I'm just a man who ^{D#m}needed someone an^{C#}d somewhere to hide \\
To keep me ^{B}alive... ^{C#} \hspace{10pt} just keep me a^{D#m}live \\
Somewhere to ^{B}hide... ^{C#} \hspace{10pt} to ^{D#m}keep me alive
\end{verse}

\begin{verse}
^{D#m}I'm not a robot ^{D#m}without emotions, ^{C#}I'm not what you see ^{C#-} ^{Dm} \\
^{D#m}I've come to help you ^{D#m}with your problems, ^{C#}so we can be free ^{C#-} ^{Dm} \\
^{D#m}I'm not a hero, ^{D#m}I'm not a savior, ^{C#}forget what you know   ^{C#-} ^{Dm}  \\
^{D#m}I'm just a man whose ^{D#m}circumstances ^{C#}went beyond his control \\
Beyond my cont^{B}rol...  ^{C#} \hspace{10pt} We all need con^{D#m}trol \\
I ^{B}need control... ^{C#} \hspace{10pt} We^{D#m} all need control
\end{verse}

\begin{prechorus}
I ^{G#}am the ^{C#}modern ^{F#}man (secret secret, I got a secret) \hspace{10pt}
Who ^{G#}hides beh^{C#}ind a ^{F#}mask (secret secret, I got a secret) \\
So ^{G#}no one ^{C#}else can ^{F#}see (secret secret, I got a secret) \hspace{10pt}
My ^{G#}true id^{C#}entity ^{D#m} \\ \\ \\
\end{prechorus}

\begin{chorus}
\begin{tabbing}
\textbf{} \=^{D#m}Domo arigato Mr. Roboto, \hspace{10pt} \=Domo... \=Domo \hspace{10pt} \=^{D#m}Domo arigato Mr. Roboto, \hspace{10pt} \=Domo... \=Domo \\
\textbf{} \>\domoarigato                  \>\domo... \>\domo              \>\domoarigato \>\domo... \>\domo \\
\textbf{} \=^{D#m}Domo arigato Mr. Roboto \hspace{30pt} \=^{C#}Domo arigato Mr. Roboto \\
\textbf{} \>\domoarigato                  \>\domoarigato  \\ 
\textbf{} \=^{D#m}Domo arigato Mr. Roboto \hspace{30pt} \=^{C#}Domo arigato Mr. Roboto  \\
\textbf{} \>\domoarigato                  \>\domoarigato \\
\textbf{Main} \hspace{10pt}  \=^{D#m}Thank you very much, Mr. Roboto \hspace{5pt} \=^{C#}for doing the jobs that nobody wants to \\
\textbf{Backup} \>Domo arigato Mr. Roboto \>Domo arigato Mr. Roboto \\
\textbf{}       \>\domoarigato            \>\domoarigato \\
\textbf{Main} \hspace{10pt} And \=^{D#m}thank you very much, Mr. Roboto, \hspace{10pt} \=^{C#}for helping me escape when I needed to \\
\textbf{Backup} \>Domo arigato Mr. Roboto \>Domo arigato Mr. Roboto \\
\textbf{}       \>\domoarigato            \>\domoarigato \\
\textbf{Main} \hspace{10pt} \=^{D#m}Thank you, thank you, \hspace{30pt} \=^{C#}thank you \\
\textbf{Backup} \>Domo arigato Mr. Roboto \>Domo arigato Mr. Roboto \\
\textbf{}       \>\domoarigato            \>\domoarigato \\
\textbf{Main} \hspace{10pt} I want to \=^{D#m}thank you... please \hspace{40pt} \=^{C#}Thank you... oooooh \\
\textbf{Backup} \>Domo arigato Mr. Roboto \>Domo arigato Mr. Roboto \\
\textbf{}       \>\domoarigato            \>\domoarigato
\end{tabbing}
\end{chorus}

\begin{interlude}
\begin{tabular}[t]{@{}lllll}
    |_{B} yeahhh! & |_{C#} & |_{D#m} & |_{D#m} & | \\
    |_{B} & |_{C#} & |_{B} & |_{C#} & | \\
    |_{D#m} & |_{D#m} & | 
\end{tabular} \\
\instruction{arpeggios} \\
\begin{tabular}[t]{@{}lll}
    |_{G#} & |_{G#} & | \\
    |_{G#} & |_{G#} & | \\
    |_{G#} The problem's plain to see & |_{G#} Too much technology & | \\
    |_{G#} Machines to save our lives & |_{G#} Machines dehumanize & | \\
    |_{G#} & |_{G#} & | \\ 
    |_{G#} & |_{G#} & |
\end{tabular}
\end{interlude}

\begin{outro}
The ^{G#}time has ^{C#}come at ^{F#}last (secret secret, I got a secret) \hspace{10pt}
To ^{G#}throw a^{C#}way this ^{F#}mask (secret secret, I got a secret) \\
Now ^{G#}every- ^{C#}one can ^{F#}see (secret secret, I got a secret) \hspace{10pt}
My ^{G#}true i^{C#}dentity... ^{D#m*-} ^{D#m*} \\
I'm ^{D#m*-}Kill- ^{D#m*}roy! ^{D#m*-}Kill- ^{D#m*}roy! ^{D#m*-}Kill- ^{D#m*}roy! ^{D#m*-}Kill- ^{D#m*}roy!
\end{outro}
