\documentclass{../../tex/bekki-leadsheet}
\begin{document}
\begin{song}{title={Heaven Is A Place On Earth}, band={Belinda Carlisle}, year={1987}, key={E}}

  \begin{intro}
    Ooh baby, do you know what that's worth? Ooh heaven is a place on earth \\
    They say in heaven love comes first.
    We'll make heaven a place on earth, ooh heaven is a place on earth
  \end{intro}

  \begin{intro}
    \begin{tabular}[t]{@{}lllll}
      |_{C#m}-_{A} & |_{B}-_{C#m} & |_{E}-_{A} & |_{B}-_{C#m} & | \instruction{x2} \\
    \end{tabular}
  \end{intro}

  \begin{verse}
    When the ^{E}night falls ^{B}down... I ^{A}wait for you, and you ^{B}come around \\
    And the ^{E}world's a^{B}live with the ^{A}sound of kids on the ^{B}street outside
  \end{verse}

  \begin{prechorus}
    ^{G} When you walk in^{A}to the room ^{G} you pull me close and we ^{A}start to move \\
    ^{F#m} And we're spinning with the ^{G}stars above
    and you ^{Em-}lift me ^{F#m}up in a ^{G-}wave of ^{A}love
  \end{prechorus}

  \begin{chorus}
    ^{C#m-}Oooh ^{A}baby do you ^{B-}know what that's ^{C#m}worth?
    ^{E-}Ooh ^{A}heaven is a ^{B-}place on ^{C#m}earth \\
    They ^{C#m-}say in ^{A}heaven ^{B-}love comes ^{C#m}first.
    ^{E-}We'll make ^{A}heaven a ^{B-}place on ^{C#m}earth,
    ^{E-}ooh ^{A}heaven is a ^{B-}place on ^{C#m}earth
  \end{chorus}

  \begin{verse}
    When I ^{E}feel a^{B}lone I ^{A}reach for you and you ^{B}bring me home \\
    When I'm ^{E}lost at ^{B}sea I ^{A}hear your voice and it ^{B}carries me
  \end{verse}

  \begin{prechorus}
    ^{G} In this world we're ^{A}just beginning ^{G} to understand the ^{A}miracle of living \\
    ^{F#m} Baby I was af^{G}raid before but I'm ^{Em-}not ^{F#m}afraid ^{G-}any- ^{A}more
  \end{prechorus}

  \begin{chorus}
    ^{C#m-}Oooh ^{A}baby do you ^{B-}know what that's ^{C#m}worth?
    ^{E-}Ooh ^{A}heaven is a ^{B-}place on ^{C#m}earth \\
    They ^{C#m-}say in ^{A}heaven ^{B-}love comes ^{C#m}first.
    ^{E-}We'll make ^{A}heaven a ^{B-}place on ^{C#m}earth,
    ^{E-}ooh ^{A}heaven is a ^{B-}place on ^{(E)}earth
  \end{chorus}

  \begin{interlude}
    \begin{tabular}[t]{@{}lllll}
      |_{E} & |_{C#m} & |_{A} & |_{B} & | \\
    \end{tabular}
  \end{interlude}

  \begin{prechorus}
    ^{G} In this world we're ^{A}just beginning ^{G} to understand the ^{A}miracle of living \\
    ^{F#m} Baby I was af^{G}raid before but I'm ^{Em-}not ^{F#m}afraid ^{G-}any- ^{A}more
  \end{prechorus}

  \begin{interlude}
    \begin{tabular}[t]{@{}lllll}
      |_{C#m}-_{A} & |_{B}-_{C#m} & |_{E}-_{A} & |_{B}-_{C#m}                  & | \\
      |_{C#m}-_{A} & |_{B}-_{C#m} & |_{E}-_{A} & |_{B}- (key change +2) _{D#m} & |
    \end{tabular}
  \end{interlude}

  \begin{chorus}
    Oooh ^{-B}baby do you ^{C#-}know what that's ^{D#m}worth?
    ^{F#-}Ooh ^{B}heaven is a ^{C#-}place on ^{D#m}earth \\
    They ^{D#m-}say in ^{B}heaven ^{C#-}love comes ^{D#m}first.
    ^{F#-}We'll make ^{B}heaven a ^{C#-}place on ^{D#m}earth
  \end{chorus}

  \begin{outro}
    \instruction{repeat and fade out} \\
    ^{F#-}Ooh ^{B}heaven is a ^{C#-}place on ^{D#m}earth
  \end{outro}

\end{song}
\end{document}
